---
title: "NYPD Crime Data"
author: "Ben Goldy"
date: "April 5, 2017"
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
---

```{r setup,echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(data.table)
library(dtplyr)
library(dplyr)
library(ggplot2)
library(spatstat)
library(gridExtra)
Felony=fread("Felony.csv")
Felony$CompStatMonth=factor(Felony$CompStatMonth,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep"))
Felony$OccurrenceMonth=factor(Felony$OccurrenceMonth,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))
Felony$Borough=as.factor(Felony$Borough)
```
#Descriptives {.tabset}
##Occurence Year
```{r summary_year,fig.width=3,fig.height=3,dpi=200 ,message=FALSE, warning=FALSE}
ggplot(Felony,
       aes(x=OccurrenceYear))+
  geom_histogram()+xlab("Year")
```

Its fairly clear that the present data is mostly from one year: 2015.

##Occurence Month
```{r summary_occmonth,fig.width=4,fig.height=3,dpi=200,message=FALSE, warning=FALSE}
ggplot(Felony,
       aes(x=OccurrenceMonth))+
  geom_histogram(stat="count")+
  xlab("Month")
```

##Reported Month
```{r summary_reportedmonth,fig.width=3.75,fig.height=3,dpi=200,message=FALSE, warning=FALSE}
ggplot(Felony,
       aes(x=CompStatMonth))+
  geom_histogram(stat="count")+
  xlab("Month")
```

##Crime Type
```{r summary_crimetype,fig.width=3,fig.height=5,dpi=200,message=FALSE, warning=FALSE}
crimetype=Felony%>%
  group_by(Offense)%>%
  mutate(Count=n())

ggplot(crimetype,
       aes(x=reorder(Offense,
                     Count)))+
  geom_histogram(stat="count")+
  xlab("Crime Type")+
  theme(
    axis.text.x=element_text(angle=90,vjust=1),
    text=element_text(size=8))
```

#Borough Interactions {.tabset}
##Total Crime by Borough
```{r borough_totalCrime,fig.width=4,fig.height=3,dpi=200,message=FALSE, warning=FALSE}
ggplot(Felony,
       aes(x=Borough))+
  geom_histogram(stat="count")+
  xlab("Borough")+
  theme(
    axis.text.x=element_text(angle=90),
    text=element_text(size=8))
```

##Borough by Crime Type
```{r borough_crimetype,fig.width=4,fig.height=5,dpi=200,message=FALSE, warning=FALSE}
ggplot(Felony,
       aes(x=Offense))+
  geom_histogram(stat="count")+
  xlab("Crime Type")+
  facet_grid(~Borough)+
  theme(
    axis.text.x=element_text(angle=90),
    text=element_text(size=8))
```

##Borough by Month
```{r summary_borough_by_month,fig.width=6,fig.height=3.5,dpi=200,message=FALSE, warning=FALSE}
ggplot(Felony,
       aes(x=OccurrenceMonth))+
  geom_histogram(stat="count")+
  xlab("Month")+
  facet_grid(~Borough)+
  theme(
    axis.text.x=element_text(angle=90),
    text=element_text(size=8))
```

#Spatial Data {.tabset}
##All Spatial Data
```{r map,fig.width=3.25,fig.height=4,dpi=200,message=FALSE, warning=FALSE}
ggplot(Felony%>%
         filter(OccurrenceYear==2015),
       aes(x=XCoordinate,
           y=YCoordinate))+
  geom_point()
```

##Colored by Borough
```{r map_color,fig.width=5,fig.height=4,dpi=200,message=FALSE, warning=FALSE}
ggplot(Felony%>%
         filter(OccurrenceYear==2015),
       aes(x=XCoordinate,
           y=YCoordinate,
           color=Borough))+
  geom_point()
```

##Colored by Precinct
```{r map_color_prcnct,fig.width=5,fig.height=4,dpi=200,message=FALSE, warning=FALSE}
ggplot(Felony%>%
         filter(OccurrenceYear==2015),
       aes(x=XCoordinate,
           y=YCoordinate,
           color=as.factor(Precinct)))+
  geom_point()
```

#Crime Patterns Overview
```{r spatialpattern,fig.width=12,fig.height=10,dpi=300}
ggplot(Felony%>%filter(Borough!=""),aes(x=XCoordinate,y=YCoordinate))+geom_density2d()+facet_grid(Borough~Offense,labeller=label_both)
```

Data was accessed: http://www.nyc.gov/html/nypd/html/analysis_and_planning/historical_nyc_crime_data.shtml
Date accessed: April 5, 2017